Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-16 doc/GMP2015/s07_problempinning.tex
Added some figures to Problem Pinning. Updated Prose

\section{Problem Pinning}
\label{sec:bodypin}

We can use DR plans to help in solving questions in designs for graphene and silica bilayers (\todo{Add Citation}). Specifically, we will look into the problem when you have a monolayer and it is underconstrained. To make this thing isostatic, there are a few methods we can apply.

\begin{figure}\centering
    \includegraphics[width=0.5\linewidth]{img/Silica}
    \caption{Example of 1 layer of a Silica Oxygen glassy structure. This can be thought of as a multi-triangle-pin qusec where the Silicon atoms are the triangles and the Oxygen atoms are the pins.}
\end{figure}

\begin{itemize}
    \item Pin together 2 underconstrained monolayers in such a way that the resulting bilayer becomes isostatic.
    \item Pin the boundary in such a way that the resulting system is isostatic.
    \item Apply a self-similarity constraint and essentially wrap the monolayer and pin it to itself (pin one edge to another in certain places)
\end{itemize}

In each case, we are specifically interested in how to pin these things so that the resultiing structure also has a small DR plan.

@@

To answer these questions, we first inroduce the structures we model the problems with:

@@

\begin{remark}
    A multi-body-pin qusec is a special case of bar-joint qusecs that we have been studying. As such, the DR planning discussed in Section \ref{dr} is unchanged and the work in Section \ref{recomb} will still go through with slight modifications.
\end{remark}

\begin{proof}
    We can replace each body that has only one pin by a single vertex. A body with 2 pins can be replaced by an edge. In general, a body with $n$ pins can be replaced by a 2-tree on $n$ vertices. When looking for a DR plan, we treat each body as trivial, so they become the leaves of our plan. The optimal completion problem and approach of Section \ref{dr} are unchanged. The optimal paramaterization problem in Section \ref{dr} now has an additional constraint that all edges in the 2-tree representation of the bodies must be removed together, not individually.
\end{proof}

In this section we will go over 2 subclasses of multi-body-pin qusecs for modeling Examples 4 and 5 in Section \ref{sec:intro}.

\begin{definition}
\label{def:body-pin}
    A body-pin qusec is a multi-body-pin qusec with the following conditions:
    \begin{itemize}
        \item Each pin is shared by at most 2 bodies
        \item No 2 bodies share more than one pin
    \end{itemize}
    Such a body-pin qusec can also be seen as a {\em body-bar qusec} where the bodies are the original bodies and each pin represents 2 bars from one body to another. For such body-bar qusecs, graphs with 1 and 2 dofs can be characterized by being $(3,4)$ and $(3,5)$ tight respectively.
\end{definition}

\begin{definition}
    A multi-triangle-pin qusec is a multi-body-pin qusec where each body is a triangle, meaning it is pinned in at most 3 places. This is also represented as a hyper qusec where each pin is a vertex and each triangle represents a tri-hyperedge. For such hyper qusecs, 1 and 2 dofs can be characterized by $(2,4)$ and $(2,5)$ tightness respectively.
\end{definition}

Body-pin qusecs are of particular interest to us in the context of Example 4 in Section \ref{intro}. Multi-triangle-pin qusec can be used to reprsent the silica bi-layers and glassy structures described in Example 5 of Section \ref{intro}, where each triangle is the junction of ``disks'' in the plane. Typically, these systems are not isostatic, so to relate the work of this paper to the systems, we define a slightly different kind of DR plan:

\begin{definition}
    A $(k,l)$ tight DR plan is one in which each child node is either a vertex maximal proper $(k,l)$ tight subgraph of the parent node or it is trivial. In our case, the trivial nodes are just the bodies.
\end{definition}

We can develop the notion of a canonical DR plan for certain $(k,l)$ tightness conditions similar to the way we did in Section \ref{sec:DRP}.

\begin{remark}
\label{rem:1dofcanon}
    For the 1 dof multi-body-pin qusecs described above, a DR plan node will follow one of the following:

    \begin{itemize}
        \item Its children will be 2 proper vertex maximal 1 dof graphs that intersect on a single body
        \item Its children will be a number of proper maximal 1 dof subgraphs, joined pairwise by at most one pin
    \end{itemize}
\end{remark}

@@

    For item 2, consider the case where we have more than 2 proper vertex maximal 1 dof subgraphs $s_1, ..., s_k, k > 2$. Then, if $k_i$ and $k_j$ are joined by $2$ pins, $k_i \Cup k_j$ would be $(3,4)$ tight and hence $k_i$ and $k_j$ are not vertex maximal.
\end{proof}

\begin{remark}
    All $(k,l)$ tight canonical DR plans are optimal. We can find such a DR plan in the same time complexity as the $(2,3)$ tight case for bar and joint qusecs discussed in Section \ref{sec:DRP}.
\end{remark}
\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.2\linewidth}\centering
    \begin{tikzpicture}[scale=0.8]
        % \tikzstyle{v}=[draw, circle, minimum size=0.1cm, scale=0.7, font=\footnotesize]
        \tikzstyle{v}=[font=\footnotesize]

@@

% \end{subfigure}
\caption{(a) is a 1 dof body-pin qusec. (b) is the corresponding body-bar qusec explained in Definition \ref{def:body-pin}. (c) is the 1 dof DR plan for the qusec. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the node in the second level. (d) is the result of adding one such body tot he bold-faced node.}

@@

\begin{proof}
    Suppose we are given a body-pin qusec $G$ and have obtained the DR plan denoted $T$. Each node of $T$ will then be a vertex maximal proper 1 dof subgraph of $G$. To make the entire graph wellconstrained, we can add a body and pin it to a node $b$ in $T$ such that the body is pinned to 2 separate children of $b$. From Remark \ref{rem:1dofcanon}, we know that the children can only be joined by a single pin or a single body, so we simply have to pin the new body to one part on each side of the pin or body. Doing so will ensure the following

@@

    Then, we can form a valid isostatic DR plan $T_b$ from $T$. In $T_b$, $b$'s children are now all of the leaf nodes of the subtree rooted at $b$ because no child of $b$ in $T$ is isostatic. Similarly, for any other node $w$ that is an ancestor of $b$, $w$'s children will be the node that leads to $b$, denoted $b'$, along with all of the other leaf nodes in the tree rooted at $w$ excluding $b'$. Then, for any node $b$ that we choose, $T_b$ is a valid DR plan. Thus, if we want to minimize the size of our DR plan, we simply need to take the $b$ that has the $T_b$ of smallest size. Running this algorithm in a brute force fashion is quadratic in the number of bodies of our given body-pin system.

@@

    % For the 2 dof case, we can do something very similar, except instead of pinning a single body 2 times to a node, we can pin another body 2 times to a node. These can be the same node, and if it is the same node, we can find a wellconstrained DR plan in quadratic time, we would just be doing the same thing as the 1 dof case.
\end{proof}

@@

\begin{proof}
    We can do a similar algorithm to the 1 dof case, except we constrain a given node 2 times (by adding 2 triangles or 2 bodies and 4 pins). This causes the nodes along the path to the given node to become well-constrained while all others will be underconstrained. Thus, our DR plan will have the same size as the 1 dof case. This is still a quadratic algorithm
\end{proof}

>>>>

\section{Application: Finding extensions of underconstrained glassy structures to isostatic}
\label{sec:bodypin}

We can use DR-plans to help in solving questions in designs for graphene and silica bilayers (\todo{Add Citation}). Specifically, we will look into the problem when you have a monolayer and it is underconstrained. Our goal is to make such a layer isostatic. This can be done in a number of ways.

\begin{figure}\centering
    \includegraphics[width=0.5\linewidth]{img/Silica}
    \caption{Example of 1 layer of a Silica Oxygen glassy structure. This can be thought of as a multi-triangle-pin qusec where the Silicon atoms are the triangles and the Oxygen atoms are the pins.}
    \label{fig:silica_glass}
\end{figure}

\begin{itemize}
    \item Pin together 2 underconstrained monolayers in such a way that the resulting bilayer becomes isostatic.
    \item Pin the boundary in such a way that the resulting system is isostatic.
    \item Build the structures by repeated subdivision to ensure they are isostatic at each layer (see Figure \ref{fig:subdivision})
\end{itemize}

We will discuss item 2 in detail in this section. In each case, we are specifically interested in how to they can be applied to get a resulting isostatic structure with a small DR-plan, so a realization can be found quickly. To answer these questions, we first inroduce the structures we model the problems with:

\begin{figure}\centering
    \begin{subfigure}{0.25\linewidth}
        \includegraphics[width=\linewidth]{img/pentl1}
    \end{subfigure}
    \begin{subfigure}{0.25\linewidth}
        \includegraphics[width=\linewidth]{img/pentl2}
    \end{subfigure}
    \begin{subfigure}{0.4\linewidth}
        \includegraphics[width=\linewidth]{img/pentl3}
    \end{subfigure}
    \caption{An example of self-similarity in the form of repeated subdivisions. Each figure follows fromt he previous due to a set subdivision rule. If each figure was guaranteed to be isostatic, then isostatic systems of arbitrary detail could be made.}
    \label{fig:subdivision}
\end{figure}

@@

@@

\begin{remark}
    A multi-body-pin qusec is a special case of bar-joint qusecs that we have been studying. As such, the DR-planning discussed in Section \ref{sec:DRP} is unchanged and the work in Section \ref{sec:recomb} will still go through with slight modifications.
\end{remark}

\begin{proof}
    We can replace each body that has only one pin by a single vertex. A body with 2 pins can be replaced by an edge. In general, a body with $n$ pins can be replaced by a 2-tree on $n$ vertices. When looking for a DR-plan, we treat each body as trivial, so they become the leaves of our plan. The optimal completion problem and approach of Section \ref{sec:DRP} are unchanged. The optimal paramaterization problem in Section \ref{sec:DRP} now has an additional constraint that all edges in the 2-tree representation of the bodies must be removed together, not individually.
\end{proof}

We now go over 2 subclasses of multi-body-pin qusecs for modeling Examples 4 and 5 in Section \ref{sec:intro}.

\begin{definition}
\label{def:body-pin}
    A body-pin qusec is a multi-body-pin qusec with the following conditions:
    \begin{itemize}
        \item Each pin is shared by at most 2 bodies
        \item No 2 bodies share more than one pin
    \end{itemize}
    Such a body-pin qusec can also be seen as a {\em body-bar graph} where the bodies are the original bodies and each pin represents 2 bars from one body to another. For such body-bar qusecs, graphs with 1 and 2 dofs can be characterized by being $(3,4)$ and $(3,5)$-tight respectively.
\end{definition}

\begin{definition}
    A multi-triangle-pin qusec is a multi-body-pin qusec where each body is a triangle, meaning it is pinned in at most 3 places. This is also represented as a hyper-graph where each pin is a vertex and each triangle represents a tri-hyperedge. For such hyper-graphs, 1 and 2 dofs can be characterized by $(2,4)$ and $(2,5)$ tightness respectively.
\end{definition}

Body-pin qusecs are of particular interest to us in the context of Example 4 in Section \ref{sec:intro}. Multi-triangle-pin qusecs can be used to reprsent the silica bi-layers and glassy structures described in Example 5 of Section \ref{sec:intro}, where each triangle is the junction of ``disks'' in the plane (se Figure \ref{fig:silica_glass}). Typically, these systems are not isostatic, so to relate the work of this paper to the systems, we define a slightly different kind of DR-plan:

\begin{definition}
    A $(k,l)$-tight DR-plan is one in which each child node is either a vertex maximal proper $(k,l)$-tight subgraph of the parent node or it is trivial. In our case, the trivial nodes are just the bodies.
\end{definition}

We can develop the notion of a canonical DR-plan for certain $(k,l)$ tightness conditions similar to the way we did in Section \ref{sec:DRP}.

\begin{remark}
\label{rem:1dofcanon}
    For the 1 dof multi-body-pin qusecs described above, a DR-plan node will follow one of the following:

    \begin{itemize}
        \item Its children will be 2 proper vertex maximal 1 dof graphs that intersect on another 1 dof graph
        \item Its children will be a number of proper maximal 1 dof subgraphs, joined pairwise by at most one pin
    \end{itemize}
\end{remark}

@@

    For item 2, consider the case where we have more than 2 proper vertex maximal 1 dof subgraphs $s_1, ..., s_k, k > 2$. Then, if $k_i$ and $k_j$ are joined by $2$ pins, $k_i \Cup k_j$ would be $(3,4)$-tight and hence $k_i$ and $k_j$ are not vertex maximal.
\end{proof}

\begin{remark}
    All $(k,l)$-tight canonical DR-plans are optimal. We can find such a DR-plan in the same time complexity as the $(2,3)$ tight case for bar and joint qusecs discussed in Section \ref{sec:DRP}.
\end{remark}

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
\begin{subfigure}{0.2\linewidth}\centering
    \begin{tikzpicture}[scale=0.8]
        % \tikzstyle{v}=[draw, circle, minimum size=0.1cm, scale=0.7, font=\footnotesize]
        \tikzstyle{v}=[font=\footnotesize]

@@

% \end{subfigure}
\caption{(a) is a 1 dof body-pin qusec. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1 dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}

@@

\begin{proof}
    Suppose we are given a body-pin qusec and its corresponding body-bar graph $G$ and have obtained the DR-plan $T$. Each node of $T$ will then be a vertex maximal proper 1 dof subgraph of $G$. To make the entire graph wellconstrained, we can add a body (vertex) and pin it (add a 2-multiedge) to a node $b$ in $T$ such that the body is pinned to 2 separate children of $b$. From Remark \ref{rem:1dofcanon}, we know that the children can only be joined by a single pin or a subgraph, so we simply have to pin the new body to the 2 bodies joined by the pin or that are not in the intersecting graph. Doing so will ensure the following:

@@

    Then, we can form a valid isostatic DR-plan $T_b$ from $T$. In $T_b$, $b$'s children are now all of the leaf nodes of the subtree rooted at $b$ because no child of $b$ in $T$ is isostatic. Similarly, for any other node $w$ that is an ancestor of $b$, $w$'s children will be the node that leads to $b$, denoted $b'$, along with all of the other leaf nodes in the tree rooted at $w$ excluding $b'$. Then, for any node $b$ that we choose, $T_b$ is a valid DR-plan. Thus, if we want to minimize the size of our DR-plan, we simply need to take the $b$ that has the $T_b$ of smallest size. Running this algorithm in a brute force fashion is quadratic in the number of bodies of our given body-pin system.

@@

    % For the 2 dof case, we can do something very similar, except instead of pinning a single body 2 times to a node, we can pin another body 2 times to a node. These can be the same node, and if it is the same node, we can find a wellconstrained DR-plan in quadratic time, we would just be doing the same thing as the 1 dof case.
\end{proof}

% THIS NEEDS SOME MORE THINKING. THERE ARE DIFFERENT TYPES OF CHILDREN NODES FOR THIS PART. NOT JUST THE TWO LISTED ABOVE

@@

\begin{proof}
    We can do a similar algorithm to the 1 dof case, except we constrain a given node 2 times (by adding 2 triangles or 2 bodies and 4 pins). This causes the nodes along the path to the given node to become well-constrained while all others will be underconstrained. Thus, our DR-plan will have the same size as the 1 dof case. This is still a quadratic algorithm.

\end{proof}
